ML parameters

### 2023-01-19 workflow/notebooks/ml-params.Rmd

---
title: "ML parameters"
date: "`r Sys.Date()`"
output: 
  github_document:
    html_preview: false
---

@@

```{r plot_dataset}
results_dat %>% 
  filter(trainfrac == 0.8, method == 'glmnet', metric == 'AUROC') %>% 
  ggplot(aes(perf_metric_value, perf_metric_name, color = outcome)) +
  geom_boxplot() +
  theme_bw() +
  facet_wrap('dataset')

results_dat %>% 
  filter(trainfrac == 0.8, method == 'glmnet', metric == 'AUROC') %>% 
  ggplot(aes(perf_metric_value, dataset, color = outcome)) +
  geom_boxplot() +
  theme_bw() +
  facet_wrap('perf_metric_name')
```

## ML method - rf vs l2 logit
```{r plot_method}
results_dat %>% 
  filter(trainfrac == 0.8, metric == 'AUROC', dataset == 'full') %>% 
  ggplot(aes(perf_metric_value, perf_metric_name, color = outcome)) +
  geom_boxplot() +
  theme_bw() +
  facet_wrap('method')

results_dat %>% 
  filter(trainfrac == 0.8, metric == 'AUROC', dataset == 'full') %>% 
  ggplot(aes(perf_metric_value, method, color = outcome)) +
  geom_boxplot() +
  theme_bw() +
  facet_wrap('perf_metric_name')
```

## metric - AUROC vs F1 score
```{r plot_metric}
results_dat %>% 
  filter(trainfrac == 0.8, method == 'glmnet', dataset == 'full') %>% 
  ggplot(aes(perf_metric_value, perf_metric_name, color = outcome)) +
  geom_boxplot() +
  theme_bw() +
  facet_wrap('metric')

results_dat %>% 
  filter(trainfrac == 0.8, method == 'glmnet', dataset == 'full') %>% 
  ggplot(aes(perf_metric_value, metric, color = outcome)) +
  geom_boxplot() +
  theme_bw() +
  facet_wrap('perf_metric_name')
```

>>>>

---
title: "ML parameters"
date: "`r Sys.Date()`"
output: 
  github_document:
    html_preview: false
  gfm:
    html_preview: false
---

@@

```{r plot_dataset}
results_dat %>% 
  filter(trainfrac == 0.8, method == 'glmnet', metric == 'AUROC', taxlevel == "OTU") %>% 
  ggplot(aes(perf_metric_value, perf_metric_name, color = outcome)) +
  geom_boxplot() +
  theme_bw() +
  facet_wrap('dataset')

results_dat %>% 
  filter(trainfrac == 0.8, method == 'glmnet', metric == 'AUROC', taxlevel == "OTU") %>% 
  ggplot(aes(perf_metric_value, dataset, color = outcome)) +
  geom_boxplot() +
  theme_bw() +
  facet_wrap('perf_metric_name') +
  labs(x="performance on held out test data")
```

## ML method - rf vs l2 logit
```{r plot_method}
results_dat %>% 
  filter(trainfrac == 0.8, metric == 'AUROC', dataset == 'full', taxlevel == "OTU") %>% 
  ggplot(aes(perf_metric_value, perf_metric_name, color = outcome)) +
  geom_boxplot() +
  theme_bw() +
  facet_wrap('method')

results_dat %>% 
  filter(trainfrac == 0.8, metric == 'AUROC', dataset == 'full', taxlevel == "OTU") %>% 
  ggplot(aes(perf_metric_value, method, color = outcome)) +
  geom_boxplot() +
  theme_bw() +
  facet_wrap('perf_metric_name') +
  labs(x="performance on held out test data")
```

## metric - AUROC vs F1 score
```{r plot_metric}
results_dat %>% 
  filter(trainfrac == 0.8, method == 'glmnet', dataset == 'full', taxlevel == "OTU") %>% 
  ggplot(aes(perf_metric_value, perf_metric_name, color = outcome)) +
  geom_boxplot() +
  theme_bw() +
  facet_wrap('metric')

results_dat %>% 
  filter(trainfrac == 0.8, method == 'glmnet', dataset == 'full', taxlevel == "OTU") %>% 
  ggplot(aes(perf_metric_value, metric, color = outcome)) +
  geom_boxplot() +
  theme_bw() +
  facet_wrap('perf_metric_name') +
  labs(y="metric optimized during model training", x="performance on held out test data")
```

## taxlevel - OTU vs genus
```{r plot_taxlevel}
results_dat %>% 
  filter(trainfrac == 0.8, method == 'glmnet', dataset == 'full', metric == 'AUROC') %>% 
  ggplot(aes(perf_metric_value, perf_metric_name, color = outcome)) +
  geom_boxplot() +
  theme_bw() +
  facet_wrap('taxlevel')

results_dat %>% 
  filter(trainfrac == 0.8, method == 'glmnet', dataset == 'full', metric == 'AUROC') %>% 
  ggplot(aes(perf_metric_value, taxlevel, color = outcome)) +
  geom_boxplot() +
  theme_bw() +
  facet_wrap('perf_metric_name') +
  labs(x="performance on held out test data")

```
